%-------------------------
% Resume in Latex
% Author : Nihal Athikkai
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

% \documentclass[letterpaper,11pt]{article}
\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Nihal Athikkai} \\ \vspace{1pt}
    \small 949-667-5926 $|$ \href{mailto:nihalathikkai1999@gmail.com}{\underline{nihalathikkai1999@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/nihal-athikkai/}{\underline{linkedin.com/in/nihal-athikkai}}  $|$ \small Bangalore
    %  $|$ \href{https://github.com/...}{\underline{github.com/nihal}}
\end{center}



\section{Professional Summary}
Software Engineer with 4+ years of experience specializing in backend development, data processing, and cloud solutions using Python, SQL, and AWS. Skilled in building scalable systems and optimizing workflows for business efficiency.


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Project Engineer}{June 2021 -- Present}
      {Wipro Ltd.}{Bangalore, Karnataka}
      \resumeItemListStart
        \resumeItem{Developed and optimized Python FastAPI backend for an internal portal used by 400+ global users to manage \emph{Quality Standard System (QSS)} scenarios and test cases, reducing approval time by {{XX}}\%.}
        \resumeItem{Implemented advanced Excel file parsing and validation logic, improving data processing efficiency by {{XX}}\%.}
        \resumeItem{Designed and deployed tracking mechanisms for scenario statuses, resource allocation, and time estimation, enhancing project visibility by {{XX}}\%.}
        \resumeItem{Migrated REST API from Flask to FastAPI, boosting API performance by 2.5x through code optimization and concurrency.}
      \resumeItemListEnd

    \resumeSubheading
      {Intern}{Dec 2019 -- Dec 2019}
      {Kerala Minerals and Metals Ltd.}{Kollam, Kerala}
      \resumeItemListStart
        \resumeItem{Conducted a detailed study of titanium-dioxide pigment production processes, gaining insights into large-scale manufacturing workflows.}
    \resumeItemListEnd

    \resumeSubheading
      {Summer Research Fellow}{May 2019 -- July 2019}
      {IIT Ropar}{Ropar, Punjab}
      \resumeItemListStart
        \resumeItem{Developed a GUI for CNC toolpath generation in the SPIF process using MATLAB App Designer, reducing toolpath generation time by {{XX}}\%.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Social Media API Service} $|$ \emph{Go, PostgreSQL, Git}}{}
          \resumeItemListStart
            \resumeItem{Developed a RESTful API service for a social media application, enabling user authentication, post creation, and interaction features.}
            \resumeItem{Implemented PostgreSQL database schema for efficient data storage and retrieval.}
            \resumeItem{Utilized Go's concurrency features to handle multiple API requests simultaneously.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Institute of Technology Calicut}{Calicut, Kerala}
      {Bachelor of Technology in Mechanical Engineering}{July 2017 -- June 2021}
    \resumeSubheading
      {Sarvodaya Central Vidyalaya}{Thiruvananthapuram, Kerala}
      {Higher Secondary Certificate, PCMC}{June. 2015 -- March 2017}
  \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, SQL (MySQL), Go} \\
     \textbf{Frameworks}{: FastAPI, Flask, Pydantic, LangChain} \\
     \textbf{Developer Tools}{: Git, Docker, VS Code, Postman} \\
     \textbf{Platforms}{: AWS (CloudFormation CDK, MWAA, EMR, RDS, Glue)} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, OpenPyXL} \\
     \textbf{Tools}{: MATLAB, SOLIDWORKS, Fusion 360}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}